literature coding explore

### 2024-04-08 reports/lit_codes_explore.qmd
update bridge and barrier plot

@@

@@

  #calculate frequency of bridges vs. barriers being mentioned in articles -- need to add biotic and abiotic indicators cols
code_freq_new <- codes_vars2 %>%
  mutate(br_pos = as.numeric(if_any(33:48, ~. == 1)), 
         ba_pos = as.numeric(if_any(49:58, ~. == 1)), 
         br_dat = as.numeric(if_any(c("Management scale aligns with system needs", "Target species data availability", "Access to advanced technology and techniques", "Data transparency and accessibility", "Abiotic data availability", "Resource use data availability"), ~. == 1)), 
         br_eco = as.numeric(if_any(c("Expected climate change induced range shifts", "Distinct habitat preferences among species in system", "Highly mobile target species", "Target species is a prey specialist", "Life history information available for target species", "Fine scale management appropriate for target species"), ~. == 1)), 
         br_soc = as.numeric(if_any(c("Resource availability", "Pre existing regulation and management institutions", "Adoption incentives for end users", "Feasibility", "Co management and communication"), ~. == 1)), 
         ba_dat = as.numeric(if_any(c("Implementation costs", "Gaps and inaccuracy", "Management scales do not align with system needs", "Model abuse", "Climate change adding uncertainty to target species habitat use"), ~. == 1)), 
         ba_eco = as.numeric(if_any(c("Need for multispecies management"), ~. == 1)), 
         ba_soc = as.numeric(if_any(c("Indirect socioeconomic consequences", "Lack of political administration permanence", "Poor communication and outreach", "Poor program implementation"), ~. == 1)))

@@

ggplot(brba_sum, aes(x = code_level, 
             y = percent,
             fill = code_brba)) +
  geom_col(width = 0.7) +
  geom_text(aes(label = percent_label),
            position = position_stack(vjust = 0.5),
            color = "black", 
            size = 5) +
  ylim(-0.6,1)+
  coord_flip() +
  scale_x_discrete() +
  scale_fill_manual(values = c("lightskyblue3", "goldenrod"), labels = c("Barrier frequency", "Bridge frequency")) +
  theme_minimal() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x =element_blank(),
        axis.text.y = element_text(size = 20, color = "black"),
        panel.grid = element_blank(),
        legend.position = c(-0.21, 0.99),
        legend.text = element_text(size = 16, color = "black"),
        strip.text.y.right = element_text(angle = 0, size = 16)) +
  geom_hline(yintercept = 0.0, linewidth = 1) + 
  labs(fill = "")+ 
  guides(fill = guide_legend(nrow = 1))
```

>>>>

#### Study taxa

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-width: 7
#| fig-height: 12

species_Gs <- codes_LU %>%
  gather(col, sp_name, species1:species16) %>%
  subset(select = sp_name)

spp_Gs_s <- species_Gs %>%
  group_by(sp_name) %>%
  filter(sp_name != "NA") %>%
  summarise(count = n()) %>%
  ungroup() %>%
  mutate(perc = count/sum(count)*100)

sp_bar <- ggplot(spp_Gs_s) +
  geom_bar(aes(x = perc, y = reorder(sp_name, perc)), fill = "dodgerblue4", width = 0.6, stat = "identity")+
  scale_x_continuous(position = "top", 
                     expand = c(0,0), 
                     limits = c(0, 23))+
  scale_y_discrete(expand = expansion(add = c(0.5,0.5))) + 
  theme(
    # Set background color to white
    panel.background = element_rect(fill = "white"),
    # Set the color and the width of the grid lines for the horizontal axis
    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
    # Remove tick marks by setting their length to 0
    axis.ticks.length = unit(0, "mm"),
    # Remove the title for both axes
    axis.title = element_blank(),
    # Only left line of the vertical axis is painted in black
    axis.line.y.left = element_line(color = "black"),
    # Remove labels from the vertical axis
    axis.text.y = element_blank(),
    # But customize labels for the horizontal axis
    axis.text.x = element_text(family = "Econ Sans Cnd", size = 12)) + 
  geom_text(aes(x = perc, y = sp_name, label = sp_name),
    hjust = 0,
    nudge_x = 0.3,
    colour = "dodgerblue4",
    family = "Econ Sans Cnd",
    size = 3.5)+
  labs(subtitle = "Percent of sum from all articles (%)") + 
  theme(plot.subtitle = element_text(
      family = "Econ Sans Cnd",
      size = 13)
  )

sp_bar
```

@@

  #calculate frequency of bridges vs. barriers being mentioned in articles -- need to add biotic and abiotic indicators cols
code_freq_new <- codes_vars2 %>%
  mutate(br_pos = as.numeric(if_any(c(33:48, 59:61), ~. == 1)), 
         ba_pos = as.numeric(if_any(49:58, ~. == 1)),
         br_dat = as.numeric(if_any(c("Management scale aligns with system needs", "Target species data availability", "Access to advanced technology and techniques", "Data transparency and accessibility", "Abiotic data availability", "Resource use data availability"), ~. == 1)), 
         br_eco = as.numeric(if_any(c("Expected climate change induced range shifts", "Distinct habitat preferences among species in system", "Highly mobile target species", "Target species is a prey specialist", "Life history information available for target species", "Fine scale management appropriate for target species", "Biotic indicators of target species presence", "Abiotic indicators of target species presence"), ~. == 1)), 
         br_soc = as.numeric(if_any(c("Resource availability", "Pre existing regulation and management institutions", "Adoption incentives for end users", "Feasibility", "Co management and communication"), ~. == 1)), 
         ba_dat = as.numeric(if_any(c("Implementation costs", "Gaps and inaccuracy", "Management scales do not align with system needs", "Model abuse", "Climate change adding uncertainty to target species habitat use"), ~. == 1)), 
         ba_eco = as.numeric(if_any(c("Need for multispecies management"), ~. == 1)), 
         ba_soc = as.numeric(if_any(c("Indirect socioeconomic consequences", "Lack of political administration permanence", "Poor communication and outreach", "Poor program implementation"), ~. == 1)))

@@

ggplot(brba_sum, aes(x = code_level, 
             y = percent,
             fill = code_brba)) +
  geom_col(width = 0.7) +
  geom_text(aes(label = percent_label),
            position = position_stack(vjust = 0.5),
            color = "black", 
            size = 5) +
  ylim(-0.7,1)+
  coord_flip() +
  scale_x_discrete() +
  scale_fill_manual(values = c("lightskyblue3", "goldenrod"), labels = c("Barrier frequency", "Bridge frequency")) +
  theme_minimal() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x =element_blank(),
        axis.text.y = element_text(size = 20, color = "black"),
        panel.grid = element_blank(),
        legend.position = c(-0.21, 0.99),
        legend.text = element_text(size = 16, color = "black"),
        strip.text.y.right = element_text(angle = 0, size = 16)) +
  geom_hline(yintercept = 0.0, linewidth = 1) + 
  labs(fill = "")+ 
  guides(fill = guide_legend(nrow = 1))
```
